Python as a machine learning language: experiences from the \textit{scikit-learn} project

### 2013-06-05 paper.tex
Added some todos

\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage[round]{natbib}
\usepackage{xcolor}

@@

Started in 2009, \textit{scikit-learn} counts a large team of volunteer
international developers mainly consisting of scientists and researchers from
various areas (e.g., machine learning, natural language processing or
neuroscience). The project also greatly benefits from many occasional
contributors proposing small code and/or documentation fixes or improvements.
Because of this large base of developers, important efforts are demanded to make
the project maintainable. In particular, we emphasize on high-quality and well-documented
code  in order to ease future developments by external contributors.

Within the past few years, the project has proven to be valuable to an  ever-
increasing user base. Its popularity can be gauged from various indicators,
including hundreds of citations in scientific papers, successes in various
machine learning challenges, or statistics from our repositories and mailing
lists.

\textcolor{red}{The rest of this text is organized as follows: in Section 2, ...}

@@

@@

\section{Application programming interface (API)}

@@

\section{Pipelines and model selection}

@@

>>>>

\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage[authoryear]{natbib}
\usepackage{xcolor}

@@

Started in 2009, \textit{scikit-learn} counts a large team of volunteer
international developers mainly consisting of scientists and researchers from
various areas (e.g., machine learning, natural language processing or
neuroscience). The project also greatly benefits from many occasional
contributors proposing small code and/or documentation fixes or improvements.
Because of this large base of developers, important efforts are demanded to make
the project maintainable. In particular, we emphasize on high-quality and well-documented
code  in order to ease future developments by external contributors.
\textcolor{red}{TODO: Mention some good coding practices (automatic testing, code
reviews, etc)}

Within the past few years, the project has proven to be valuable to an  ever-
increasing user base. Its popularity can be gauged from various indicators,
including hundreds of citations in scientific papers, successes in various
machine learning challenges, or statistics\footnote{\textcolor{red}{Cite some
statistics here.}} from our repositories and mailing lists.

\textcolor{red}{TODO: The rest of this text is organized as follows: in Section 2, ...}

@@

\section{API}

@@

@@

\subsection{Composition}

@@

\subsection{Model selection}
